---
title: "notes"
author: "Douglas Yu"
date: "2023-08-24"
output: html_document
editor_options: 
  chunk_output_type: console
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

explanation for how to publish a bookdown project to github.io
https://community.rstudio.com/t/hosting-bookdown-in-github/20427/7

how to edit and publish
edit *.Rmd files
git commit and push those changes.  this is only for version control of the *.Rmd files
go to the Build tab and click on arrow next to Build Book and click on bookdown::gitbook
This will cause changes to files in the /docs directory.
git commit and push those changes. In about a minute, the dougwyu.github.io pages will change.

```{r}
# install.packages("remotes")
remotes::install_github("rlesur/klippy")

if (!require("BiocManager", quietly = TRUE))
    install.packages("BiocManager")
BiocManager::install(version = "3.17")
BiocManager::install(c("GenomicFeatures", "AnnotationDbi"))
BiocManager::install(c("phyloseq"))
```

