---
title: "notes"
author: "Douglas Yu"
date: "2023-08-24"
output: html_document
editor_options: 
  chunk_output_type: console
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

This bookdown project is hosted here:
<https://github.com/dougwyu/6013A-Bioinformatics>

and is deployed here:
<https://dougwyu.github.io/6013A-Bioinformatics/index.html>

```{r}
git2r::repository(here::here())
```


The code for the practical instructions is hosted on Doug's Github account at

  https://github.com/dougwyu/6013A-Bioinformatics

which was forked from Phil and Ellen's original version at

  https://github.com/UEABIO/6013A-Bioinformatics

I have cloned https://github.com/dougwyu/6013A-Bioinformatics to my local Mac (in this directory).

To edit, push to GitHub, and publish on github.io, do this:

  1. open the project (click on 6013A-Bioinformatics.Rproj)
  
  2. edit *.Rmd files
  	index.Rmd # Section 1
  	01-intro.Rmd # Section 2
  	02_BLAST.Rmd # Section 3
  	
  3. git commit and push those changes.  This is only for version control, i.e. this only pushes the changes to https://github.com/dougwyu/6013A-Bioinformatics
  
  4. go to the Build tab and click on arrow next to Build Book and click on bookdown::gitbook
  
  	This will cause changes to files in the /docs directory.
  
  5. git commit and push those changes. In about a minute, the dougwyu.github.io pages will change.


An explanation for how to publish a bookdown project to github.io
https://community.rstudio.com/t/hosting-bookdown-in-github/20427/7


Use my Github account to sign into the correct Posit Cloud account for the class. 





Reference code chunk for installing some of the more obscure R packages
```{r}
remotes::install_github("rlesur/klippy")

if (!require("BiocManager", quietly = TRUE))
    install.packages("BiocManager")
BiocManager::install(version = "3.17")
BiocManager::install(c("GenomicFeatures", "AnnotationDbi"))
BiocManager::install(c("phyloseq"))
```


```{r install packages, eval=FALSE}
remotes::install_bioc("Biostrings")  
remotes::install_github("mhahsler/rBLAST")  
install.packages("taxonomizr")
#install.packages("seqinr")  
```
