---
title: "BIO-6013A/7004A, Bioinformatics Skills I and II"
author: "Philip Leftwich, Ellen Bell, Douglas Yu"
date: "`r Sys.Date()`"
site: bookdown::bookdown_site
output: bookdown::gitbook
documentclass: book
bibliography: [book.bib, packages.bib]
biblio-style: apalike
link-citations: yes
github-repo: rstudio/bookdown-demo
description: "This is very brief introduction to some of the basic skills required to handling sequencing data for Bioinformatics"
always_allow_html: true
---

# Introduction

This is a very short introduction to some of the processes and tools we use when working in bioinformatics.

This is not meant to be anywhere near comprehensive; you will be shown a few of the fundamentals, and one walk-through of a single bioinformatics 'pipeline'.

One of the *main* differences between Bioinformatics and the data analysis you have done before is the **size** of the data. Bioinformatics usually deals with sequencing data, and this data has large file sizes.

Handling **big data** means you need to know how to operate on a supercomputer so we will be learning a little bit of Linux, processing **big** data into **small** data and then exporting into R to make some more amazing data visuals and interpret our findings!

This bookdown project is hosted here:

<https://github.com/dougwyu/6013A-Bioinformatics>

and is deployed here:

<https://dougwyu.github.io/6013A-Bioinformatics/index.html>

**DON'T** worry if you don't understand everything

**DO** ask lots of questions!

```{r include=FALSE}
library(tidyverse)
# automatically create a bib database for R packages
knitr::write_bib(c(
  .packages(), 'bookdown', 'knitr', 'rmarkdown'
), 'packages.bib')

knitr::opts_chunk$set(message=FALSE, warning=FALSE, eval=FALSE)
```

```{r klippy, echo=FALSE, eval=TRUE, include=TRUE}
klippy::klippy(c('r', 'bash'), position = c('top', 'right'), tooltip_message = 'copy to clipboard', tooltip_success = 'Copied!')
```
